### 2021-07-09 docs/manuscript/manuscript.tex
fix error

 \item {\bf Mutate GRNs randomly and evaluate fitness again.} Mutations
included changes in the  numerical values of degradation and diffusion
parameters and interaction strengths, and addition and removal of interactions
among genes and between the genes and the morphogen. If fitness of the mutated
GRN was greater or equal than that of the previous GRN, mutated GRN was saved
and the cycle continued from step 2. This cycle was repeated 50000, and a GRN
sampled at a given step and with a fitness score ≥ 0.95 was saved to a file as
long as its associated topology had not been sampled in previous steps.

>>>>

 \item {\bf Mutate GRNs randomly and evaluate fitness again.} Mutations
included changes in the  numerical values of degradation and diffusion
parameters and interaction strengths, and addition and removal of interactions
among genes and between the genes and the morphogen. If fitness of the mutated
GRN was greater or equal than that of the previous GRN, mutated GRN was saved
and the cycle continued from step 2. This cycle was repeated 50000 times, and a GRN
sampled at a given step and with a fitness score ≥ 0.95 was saved to a file as
long as its associated topology had not been sampled in previous steps.
